Labor Markets and Technological Change: Evidence from Electronic Health Records

### 2022-04-11 Paper/Paper.tex

\begin{figure}
    \centering
    \includegraphics{obj}
    \caption{Caption}
    \label{fig:my_label}
\end{figure}
Another way to examine whether physicians are switching settings in a vague sense is to see whether the zip codes in which the physicians work is changing. Estimates for this outcome variable are shown in

@@

@@

>>>>

\begin{figure}[ht]
    \centering
    \caption{Effect of EHR Exposure on Fraction of Patients Seen in Office}
    \includegraphics[scale=.57]{Objects/officefrac_plot.pdf}
    \label{fig:officefirst}
\end{figure}

\begin{figure}[ht]
    \centering
    \caption{Effect of EHR Exposure on Likelihood of Working in Office}
    \includegraphics[scale=.57]{Objects/officeind_plot.pdf}
    \label{fig:officesecond}
\end{figure}

Another way to examine whether physicians are switching settings in a vague sense is to see whether the zip codes in which the physicians work is changing. Estimates for this outcome variable are shown in

\begin{figure}[ht]
    \centering
    \caption{Effect of EHR Exposure on Likelihood of Changing Zip Codes}
    \includegraphics[scale=.57]{Objects/zip_plot.pdf}
    \label{fig:zip}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \caption{Effect of EHR Exposure on Patient Count}
    \includegraphics{Objects/patient_plot.pdf}
    \label{fig:patient}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \caption{Effect of EHR Exposure on Claim Count}
    \includegraphics{Objects/claim_plot.pdf}
    \label{fig:claim}
\end{figure}
